### 2017-05-08 paper1.tex
Add files via upload

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

@@

By convolving modeled spectral radiances by a dome transmittance curve, the correction method presented in this study accounts for dome effects. Thus, correction magnitudes include both atmospheric and effects from spectrally non-uniform dome transmittance (and, crudely, emissivity effects, as modeled radiances are calculated with $\epsilon$ = 0.95 and include a reflected L\textsubscript{sky} component). While the individual effects are difficult to separate, temperature dependent differential dome effects are visible in correction magnitudes as a persistent minor positive correction in winter. Relative to T\textsubscript{calib}, colder T\textsubscript{emiss} in winter results in a larger dome effects. This manifests in artificially low T\textsubscript{hem, b} and increased wintertime correction magnitudes. Additionally, modeled irradiances include a reflected downwelling component, which, although small, is sensitive to T\textsubscript{air} and humidity profiles above the sensor height. Because this data was not consistently measured, mid-latitude summer and winter standard atmospheric profiles were supplemented. The climate of Basel is characterized by mild, humid winters (K\"oppen classification: Cfb). As a result, above-sensor T\textsubscript{air} and humidity values are likely underestimated by the standard wintertime atmosphere, reducing the modeled at-sensor reflected component of downwelling longwave in winter and the overall modeled at-sensor signal. This results in an increase in derived T\textsubscript{hem, r} and correction magnitudes as measured irradiances are matched with irradiances modeled at slightly higher T\textsubscript{surf} to make up for the underestimated at-sensor L\textsubscript{sky} signal.

>>>>

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in Figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

@@

By convolving modeled spectral radiances by a dome transmittance curve, the correction method presented in this study accounts for dome effects. Thus, correction magnitudes include both atmospheric effects and effects from spectrally non-uniform dome transmittance (and, crudely, emissivity effects, as modeled radiances are calculated with $\epsilon$ = 0.95 and include a reflected L\textsubscript{sky} component). While the individual effects are difficult to separate, temperature dependent differential dome effects are visible in correction magnitudes as a persistent minor positive correction in winter. Relative to T\textsubscript{calib}, colder T\textsubscript{emiss} in winter results in a larger dome effects. This manifests in artificially low T\textsubscript{hem, b} and increased wintertime correction magnitudes. Additionally, modeled irradiances include a reflected downwelling component, which, although small, is sensitive to T\textsubscript{air} and humidity profiles above the sensor height. Because this data was not consistently measured, mid-latitude summer and winter standard atmospheric profiles were supplemented. The climate of Basel is characterized by mild, humid winters (K\"oppen classification: Cfb). As a result, above-sensor T\textsubscript{air} and humidity values are likely underestimated by the standard wintertime atmosphere, reducing the modeled at-sensor reflected component of downwelling longwave in winter and the overall modeled at-sensor signal. This results in an increase in derived T\textsubscript{hem, r} and correction magnitudes as measured irradiances are matched with irradiances modeled at slightly higher T\textsubscript{surf} to make up for the underestimated at-sensor L\textsubscript{sky} signal.
